\subsection{Key Personnel}
\subsubsection{WP0}

%\noindent
\Dparagraph{Alfons Weber} is the PI of the current DUNE pre-production project and has been the PI and PM of the previous preparatory grant. He has extensive experience in all aspects of accelerator neutrino experiments and has has a long history in their construction and exploitation from MINOS (PMTs, far detector electronics, beam and oscillation analysis convener) over T2K (near detector and electronics convener, cross section convener) and Laguna-LBNO (IB chair) to LBNE/DUNE (UK PI, beam optimisation leader, near detector convener, member of the executive board).

\Dparagraph{Roy Preece} is the current project manager for LBNF/DUNE. He has previously worked as the T2K near detector installation manager in Japan, was in charge of delivering the MICE superconductive magnets and has most recently been the project manager for LZ and the DUNE pre-production project. 
{\color{red}Add his training. Should we mention that he is leaving?}

\Dparagraph{Gary Barker} is deputy PI with special responsibility for the DUNE part of the overall project. He has been a member of T2K and Laguna-LBNO and been in DUNE from the very beginning. He is the chair of the LBNF/DUNE Institutional Board. {\color{red} need to add his experience.}

\subsubsection{WP1}

\Dparagraph{Andy Blake} is awesome and the manager of WP1. He is an expert in the analysis of neutrio data and ...

\Dparagraph{Costas Andreopoulos} is the brain behind GENIE and VaLOR. 

\Dparagraph{John Marshall} is good with computers. brain behind Pandora, 


\Dparagraph{Pete Clarke} knows the GRID

\subsubsection{WP2}

\Dparagraph{Giles Barr} 

\Dparagraph{Simon Peeters} 

\Dparagraph{David Cussans} 

\Dparagraph{An Other} (key technical and management people)


\subsubsection{WP3}

\Dparagraph{\bf Justin Evans} is WP manager

\Dparagraph{\bf Alan Grant} is WP engineer

\Dparagraph{\bf Christos Touramanis} is the consortium leader

\Dparagraph{An Other} (key technical and management people)



