\subsection{WP3 APAs (8 pages)}

\subsubsection{Introduction}

Why are we doing this?
We did protoDUNE, so we know we can deliver.


\subsubsection{Work plan}

Overall schedule outline.

\subsubsection{WP3.0 Management}
\paragraph{WP3.0.1 Overall management}
\paragraph{WP3.0.2 Quality management}
QC is incorporated into all the WBS below.
We have a QC manager who manages QC.
I must face the inevitability that I need to understand the difference between QA and QC.

\paragraph{WP3.0.3 Procurement management}
Work with Roy and STFC. Business stuff: engagement with industry. UK industry is great and we should definitely pander to the outdated concept of sovereignty by preferentially using British businesses. Though we'll obey EU procurement law. If we're still in the EU.

Procurement people in Universities.
We'll start by placing procurement orders for 75 copies of things, and wait for the collaboration to make the decision on the second module.

\paragraph{WP3.0.4 Communication with the international collaboration}
Justin will go to lots of meetings.

\subsubsection{WP3.1 APA mechanics}
\paragraph{WP3.1.1 APA frames}
Need to lay out the precise effort requirements for QC. Two producers, each producing an APA every 15 days (which puts us ahead of critical path). Each 30 days, a bunch of people will spend ~5 days doing QC in the companies.

State all the QC requirements of the frame. Point out that frame design is still being finalised, but there are no show-stoppers (the only risk is delay).

\paragraph{WP3.1.2 Mesh panels}
Do all this in the first four years. We're mitigating risk by using mesh panels on APA 7.

\paragraph{WP3.1.3 APA parts procurement}

Combs. Comb bases. Wire. Glue. Solder. Protection panels that go on the outside prior to shipping. Tie in with the materials management WP to ensure the rate is correct. This part is all about finding the suppliers.

\subsubsection{WP3.2 Electrical components}
\paragraph{WP3.2.1 PCB and cable procurement}
Explain how many different types of boards there are.
State the QC requirements.
All done in the first four years.

\paragraph{WP3.2.2 PCB and cable reception testing}
Need to talk to PSL.

\paragraph{WP3.2.3 Board assembly}
Need to talk to PSL.

\subsubsection{WP3.3 Factory setup}
\paragraph{WP3.3.1 Factory infrastructure}
\paragraph{WP3.3.2 Winding machines}
\paragraph{WP3.3.3 Process carts and jigs}

\subsubsection{WP3.4 Factory operations}
\paragraph{WP3.4.1 Factory management}
\paragraph{WP3.4.2 Factory maintenance}
\paragraph{WP3.4.3 Materials management}
\paragraph{WP3.4.4 APA production}
\paragraph{WP3.4.5 APA quality control and documentation}

\subsubsection{WP3.5 APA shipping}
\paragraph{WP3.5.1 Shipping boxes}
Storage before ITF.


\paragraph{WP3.5.2 Shipping management}

\subsubsection{WP3.6 Integration}
\paragraph{WP3.6.1 Contributions to technical coordination}
\paragraph{WP3.6.2 Detector studies}
\paragraph{WP3.6.3 APA reception testing at SURF}

\subsubsection{Deliverables and Milestones}

\subsubsection{Business Case}
